{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-29 paper/tex/sections/discussion.tex
Floor feedback: discussion

\textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ and should not be extrapolated outside this region. However, in the Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$. Therefore, for our study we had to reassign any metallicities outside of COMPAS' range. We expect that stellar winds will be reduced to such a degree that they are effectively zero for any metallicity below the minimum. Hence we set any metallicity below the minimum, $Z = 10^{-4}$, equal to the $Z = 10^{-4}$. Similarly, DCO formation is less efficient at high metallicity \citep[e.g.][]{Broekgaarden+2021} and so exploring metallicities above the COMPAS maximum is unlikely to contribute significantly to the observed rate. Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).

>>>>

\textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ (due to the limits of the underlying models in \citet{Hurley+2000}) and should not be extrapolated outside this region. However, in the Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$. Therefore, for our study we had to reassign any metallicities outside of COMPAS' range. We expect that stellar winds will be reduced to such a degree that they are effectively zero for any metallicity below the minimum. Hence we set any metallicity below the minimum, $Z = 10^{-4}$, equal to the $Z = 10^{-4}$. Similarly, DCO formation is less efficient at high metallicity \citep[e.g.][]{Broekgaarden+2021} and so exploring metallicities above the COMPAS maximum is unlikely to contribute significantly to the observed rate. Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
